Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2022-01-22 FDT2020/main-section.tex
finished minor comments - mostly

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given an integral vector $\tilde{x}$ in the dominant of an LP relaxation ($\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$) for an IP instance that has integrality gap $g < \infty$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time such that $\bar{x}\leq \tilde{x}$.\end{lemma}
Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$.
%\cindy{I added the caveat that the instance has a finite integrality gap and made it a little more self-contained.  Is it OK?}
Hence, we can assume in the proof below that $\tilde{x}_i= 0$ for $i=t+1,\ldots,n$. 
%\arash{I also made a change based on the change above}\cindy{Thanks!}
\subsection{Proof of Lemma \ref{domlemma}: The DomToIP Algorithm}

We introduce an algorithm that builds a solution from the input integral point $\tilde{x}$. It finalizes a binary value for each variable iteratively, starting from the first coordinate and ending at the $t$-th coordinate.
%Any coordinate that is $0$ in $\tilde{x}$ remains $0$ in the solution.
In iteration $\ell\in \{0,\ldots,t-1\}$, if $\tilde{x}_{\ell+1}=1$, the algorithm reduces the $\ell + 1$st coordinate of the solution to $0$ if there is an LP-feasible point $x'$ that respects the decisions made so far, and has $x'_{\ell}=0$. Intuitively, we can fix this coordinate to $0$ in the partial solution and still set the remaining coordinates to find the solution promised in Lemma~\ref{domlemma}.
\arash{A caution here: the phrase if possible a bit vague here. We round down to zero, if there is feasible solution to LP (so a point in $P(I)$, such that the first $\ell$ coordinates of it are all equal to the point $x^{(\ell)}$ that we have in iteration $\ell$ and its $\ell+1$-th coordinate is 0}.
\cindy{Yes.  I was just trying to give intuition. In particular, I was trying to distinguish Dom2IP that starts with an integral vector, where we push $1$s down, from FDT, where we start with a fractional vector and progressively set components to binary values. Do you think the above version is OK?}
More specifically, in iteration $\ell\in \{0,\ldots,t-1\}$ we produce $x^{(\ell)}\in \dom(P)$ such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$. These $\ell$ components will not change for the remainder of the algorithm.
%We run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
%\cindy{I think the previous sentence also added to my confusion before (along with the term ``fix'' which I have replaced).  After $\ell$ iterations the first $\ell$ components are integer, but they were integer before.  Did you intend to say that we finalize a 0-1 value for the first $\ell$ coordinates?}

@@

We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we set $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $z^*\in \LP^{(\ell+1)}$. Also, $z^*\in P$. By Theorem \ref{CV2} and Observation \ref{dom01}, there exists $\tilde{z}^i\leq 1$ in $\dom(S)$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$. We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$.
So for $j\in [n]$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i\in [k]$. This implies $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $z\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $z\in \IP^{(\ell+1)}$. If $z\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is the minimum index (between $1$ and $\ell$) satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of the DomToIP algorithm. We have $z\leq x^{(\ell+1)}\leq x^{(j)}$.
%\cindy{I certainly believe you and Bob on correctness, and I was convinced of the correctness of (and wrote a bunch of the proofs for) the earlier version.  But while I have a little time, I'll point out places where I was confused (and hence a reader might be). This last statement I don't see right away.  It doesn't seem that $x^{(\ell+1)}\leq x^{(j)}$ in general when $j < \ell + 1$. It seems that in general, for a fractional element $x_q$, DomToIP can round the $q$th element either up or down depending on whether it's OK to round down (future feasibility assured).  So it seems that $x^j$, which is more fractional, could have some elements smaller and some elements larger than the more integral $x^{(\ell+1)}$.  This confusion carries forward to the assertion that $z$ is a feasible solution to $\HelperLP(x^{(j-1)})$.  Suppose that $x_q = .2$ for some $q < \ell$ and Dom2IP rounded the $q$th element up to $1$. $\HelperLP(x^{q})$ has a constraint $z_q \le 0.2$, but subsequent LPs, such as $\HelperLP(x^{(\ell)})$ have a constraint $x_q = 1$. So the later LP solutions may not be feasible for the earlier ones.}
We also have $x^{(j)}_j=1$ which implies when we solved $\HelperLP(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $z$ is a feasible solution to $\HelperLP(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $z\in \IP^{(\ell+1)}$.

@@

The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $\bar{x}$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. In each level of the tree, the algorithm maintain a conic combination of points with the properties mentioned above. Leaves of the FDT tree contain integral solutions
%with integer values for all the $x$ variables
that dominate a point in $P$. In Lemma~\ref{domlemma} we saw how to turn these into points in $S$.

@@

		\begin{equation}\label{splitting}
		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}.
		\end{equation}
		For $j=0,1$, let $x^j = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}\tilde{x}^i$. Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$. Note that $\lambda_0+\lambda_1 =1/g$. Since $g\leq 1$, Constraint (\ref{mulitplier-packing}) is satisfied. Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}). Also, for $j=0,1$ we have
		\begin{equation}
		Ax^j= \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} A\tilde{x}^i  \geq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
		\end{equation}
		Hence, Constraints (\ref{feasibility}) holds. Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$. The rest of the constraints trivially hold. 
	\end{cproof}
	This concludes the proof of Lemma \ref{LPClemma}.	
\end{proof}

@@

	We now show that $\hat{x}^0$, $\hat{x}^1$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions. Note that conditions (i), (ii), (iii), and (v) are trivially satisfied. Thus we only need to show (iv) holds. We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq x'_j$. If $j=\ell,\ldots,t$, then this clearly holds. Hence, assume $j\leq \ell-1$. By the property of $x'$ we have $x'_j\in \{0,1\}$. If $x'_j= 0$, then by Constraint (\ref{packing}) we have $\bar{x}^0_j = \bar{x}^1_j=0$. Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds. Otherwise if $x'_j = 1$, then we have
	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
	Therefore (v) holds.
\end{proof}

\paragraph{Growing and Pruning FDT tree.} The FDT algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm. The nodes in $L_i$ correspond to the nodes in level $i$ of the FDT tree. The leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.

\begin{lemma}\label{prune}
	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $x\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$:
	(a) If $x\in L_i$, then $x_j \in \{0,1\}$ for $j\in [i]$, i.e. the first $i$ coordinates of a solution in level $i$ are integral, (b) $\sum_{[x,\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$, (c) $\sum_{[x,\lambda]\in L_i}\lambda x \leq x^*$, (d) $|L_i|\leq t$.
\end{lemma}
\begin{proof}
	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm. Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $x^*$ and multiplier 1. All the requirements in the lemma are satisfied for this choice.

	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$. Let the solutions in $L_i$ be $x^j$ for $j\in [k]$ and $\lambda_j$ be their multipliers, respectively. For each $j\in[k]$ if $x^j_{i+1}=1$ we add the pair $(x^j,\lambda_j)$ to $L'$. Otherwise,	applying Lemma \ref{round-up} (setting $x'= x^j$ and $\ell = i+1$) we can find $x^{j0}$, $x^{j1}$, $\lambda^0_j$ and $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}. Add the pairs  $(x^{j0} ,\lambda_j\lambda^0_j)$ and  $(x^{j1} ,\lambda_j\lambda^1_j)$ to $L'$. It is easy to check that set $L'$ is a suitable candidate for $L_{i+1}$, i.e. set $L'$ satisfies (a), (b) and (c). However we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$. We call the following linear program $\prun(L')$. Let $L' = \{[x^1,\gamma_1],\ldots,[x^{|L'|},\gamma_{|L'|}]\}$. The variables of $\prun(L')$ are scalar variables $\theta_j$ for each node $j$ in $L'$.  
		\begin{equation}
		\prun(L')\quad\quad\quad \{\max \sum_{j=1}^{|L'|} \theta_j\;:\; \sum_{j=1}^{|L'|} \theta_j x^j_i\leq x^*_i \mbox{ for $i\in [t]$},\; \theta\geq 0 \}
		\end{equation}

@@

	\paragraph{From leaves of FDT to feasible solutions.}
	For the leaves of the FDT tree,  $L_t$, we have that every solution $x$ in $L_t$ has $x\in\{0,1\}^n$ and $x\in \dom(P)$. By applying Lemma \ref{domlemma} we can obtain a point $x'\in S$ such that $x'\leq x$. This concludes the description of the FDT algorithm and proves Theorem \ref{binaryFDT}. See Algorithm \ref{FDTFull} for a summary of the FDT algorithm.

@@

\begin{proof}
	Consider the following LP with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
	\begin{align}
	\quad\quad& \max\quad \;\sum_{j=0,1,2}\lambda_j\\
	&\;\text{s.t.} \quad x^j(\delta(U))\geq 2\lambda_j \;& \mbox{ for $\emptyset \subset U \subset V$, and $j=0,1,2$} \label{feasibility2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq 2\lambda_j\; &\mbox{ for $j=0,1,2$}\label{bound2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^j_e =j\cdot \lambda_j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq \lambda_j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1+x^2 \leq x\label{packing2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1,\lambda_2 \geq 0
	\end{align}	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above. Let $\hat{x}^{j}={x^j}/{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$. If $\gamma_j=0$, let $\hat{x}^{j}=0$. Observe that  (ii), (iii), (iv), and (v) are satisfied with this choice. We can also show that $\gamma_0+\gamma_1+\gamma_2\geq {1}/{g(\2ec)}$, which means that (i) is also satisfied. The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 1$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.	
	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1+\gamma_2\geq \frac{1}{g(\2ec)}$.
	\end{claim}
	\begin{cproof}
		Suppose for contradiction $\sum_{j=0,1,2}\gamma_j = \frac{1}{g(\2ec)} - \epsilon$ for some $\epsilon >0$. Construct graph $G'$ by removing edge $f$ with $x_f\geq 1$ and replacing it with a path $P_f$ of length $\ceil{\frac{2}{\epsilon}}$. Define $x'_h = x_h$ for each edge $h$ such that $x_h<1$. For each $h\in P_f$ let $x'_h= x_f$ for all $f$ with $x_f\geq 1$. It is easy to check that $x'\in \subtour(G')$. By Theorem \ref{CV2} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multi-subgraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that 
		$\sum_{i=1}^{k}\theta_i \chi^{F'_i}\leq g(\2ec)x'$.

>>>>

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given an integral vector $\tilde{x}$ in the dominant of an LP relaxation ($\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$) for an IP instance that has integrality gap $g < \infty$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time such that $\bar{x}\leq \tilde{x}$.\end{lemma}
Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since one can obtain an integer point in $\dom(P)$ by numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$.
%\cindy{I added the caveat that the instance has a finite integrality gap and made it a little more self-contained.  Is it OK?}
Hence, we can assume in the proof below that $\tilde{x}_i= 0$ for $i=t+1,\ldots,n$. 
%\arash{I also made a change based on the change above}\cindy{Thanks!}
\subsection{Proof of Lemma \ref{domlemma}: The DomToIP Algorithm}

We introduce an algorithm that builds a solution from the input integral point $\tilde{x}$. It finalizes a binary value for each variable iteratively, starting from the first coordinate and ending at the $t$-th coordinate.
%Any coordinate that is $0$ in $\tilde{x}$ remains $0$ in the solution.
In iteration $\ell\in \{0,\ldots,t-1\}$, if $\tilde{x}_{\ell+1}=1$, the algorithm reduces the $\ell + 1$st coordinate of the solution to $0$ if there is an LP-feasible point $x'$ that respects the decisions made so far, and has $x'_{\ell}=0$. Intuitively, we can fix this coordinate to $0$ in the partial solution and still set the remaining coordinates to find the solution promised in Lemma~\ref{domlemma}.\arash{A caution here: the phrase if possible a bit vague here. We round down to zero, if there is feasible solution to LP (so a point in $P(I)$, such that the first $\ell$ coordinates of it are all equal to the point $x^{(\ell)}$ that we have in iteration $\ell$ and its $\ell+1$-th coordinate is 0}\cindy{Yes.  I was just trying to give intuition. In particular, I was trying to distinguish Dom2IP that starts with an integral vector, where we push $1$s down, from FDT, where we start with a fractional vector and progressively set components to binary values. Do you think the above version is OK?} More specifically, in iteration $\ell\in \{0,\ldots,t-1\}$ we produce $x^{(\ell)}\in \dom(P)$ such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$. These $\ell$ components will not change for the remainder of the algorithm.
%We run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
%\cindy{I think the previous sentence also added to my confusion before (along with the term ``fix'' which I have replaced).  After $\ell$ iterations the first $\ell$ components are integer, but they were integer before.  Did you intend to say that we finalize a 0-1 value for the first $\ell$ coordinates?}

@@

We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we set $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $z^*\in \LP^{(\ell+1)}$. Also, $z^*\in P$. By Theorem \ref{CV2} and Observation \ref{dom01}, there exists $\tilde{z}^i\leq 1$ in $\dom(S)$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$. We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$.
So for $j\in [n]$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i\in [k]$. This implies $\tilde{z}^i\leq x^{(\ell+1)}$ for $i\in [k]$. Hence, there exists $z\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $z\in \IP^{(\ell+1)}$. If $z\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is the minimum index (between $1$ and $\ell$) satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of the DomToIP algorithm. We have $z\leq x^{(\ell+1)}\leq x^{(j)}$.
%\cindy{I certainly believe you and Bob on correctness, and I was convinced of the correctness of (and wrote a bunch of the proofs for) the earlier version.  But while I have a little time, I'll point out places where I was confused (and hence a reader might be). This last statement I don't see right away.  It doesn't seem that $x^{(\ell+1)}\leq x^{(j)}$ in general when $j < \ell + 1$. It seems that in general, for a fractional element $x_q$, DomToIP can round the $q$th element either up or down depending on whether it's OK to round down (future feasibility assured).  So it seems that $x^j$, which is more fractional, could have some elements smaller and some elements larger than the more integral $x^{(\ell+1)}$.  This confusion carries forward to the assertion that $z$ is a feasible solution to $\HelperLP(x^{(j-1)})$.  Suppose that $x_q = .2$ for some $q < \ell$ and Dom2IP rounded the $q$th element up to $1$. $\HelperLP(x^{q})$ has a constraint $z_q \le 0.2$, but subsequent LPs, such as $\HelperLP(x^{(\ell)})$ have a constraint $x_q = 1$. So the later LP solutions may not be feasible for the earlier ones.}
We also have $x^{(j)}_j=1$ which implies when we solved $\HelperLP(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $z$ is a feasible solution to $\HelperLP(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $z\in \IP^{(\ell+1)}$.

@@

The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $\bar{x}$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. In each level of the tree, the algorithm maintains a conic combination of points with the properties mentioned above. Leaves of the FDT tree contain integral solutions
%with integer values for all the $x$ variables
that dominate a point in $P$. In Lemma~\ref{domlemma} we saw how to turn these into points in $S$.

@@

		\begin{equation}\label{splitting}
		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}.
		\end{equation}
		For $j=0,1$, let $x^j = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}\tilde{x}^i$. Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$. Note that $\lambda_0+\lambda_1 =1/g$. Since $g\leq 1$, Constraint (\ref{mulitplier-packing}) is satisfied. Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}). Also, for $j=0,1$ we have
		\begin{equation}
		Ax^j= \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} A\tilde{x}^i  \geq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
		\end{equation}
		Hence, Constraints (\ref{feasibility}) holds. Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is  $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$. Finally, we have $x^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g}\tilde{x}^i \leq \sum_{i\in[k], \tilde{x}^i_\ell = j}\theta_i\tilde{x}\leq \sum_{i\in[k], \tilde{x}^i_\ell = j}\theta_i = \lambda^j$. So all the constraints hold.
	\end{cproof}
	This concludes the proof of Lemma \ref{LPClemma}.	
\end{proof}

@@

	We now show that $\hat{x}^0$, $\hat{x}^1$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions. Note that conditions (i), (ii), (iii), and (v) are satisfied directly from the  fact that $\bar{x}^0,\bar{x}^1,\gamma_0$ and $\gamma_1$ satisfy these conditions. Thus we only need to show (iv) holds. We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq x'_j$. If $j=\ell,\ldots,t$, the inequality is satisfied since $\hat{x}^i_j = \bar{x}^i_j$ for $i=0,1$ and property (iv) holds for $\bar{x}^0$ and $\bar{x}^1$. Hence, assume $j\leq \ell-1$. By the property of $x'$ we have $x'_j\in \{0,1\}$. If $x'_j= 0$, then by Constraint (\ref{packing}) we have $\bar{x}^0_j = \bar{x}^1_j=0$. Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds. Otherwise if $x'_j = 1$, then we have
	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
	Therefore (v) holds.
\end{proof}

\paragraph{Growing and Pruning the FDT tree.} The FDT algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm. The nodes in $L_i$ correspond to the nodes in level $i$ of the FDT tree. The leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.

\begin{lemma}\label{prune}
	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $x\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$:
	(a) If $x\in L_i$, then $x_j \in \{0,1\}$ for $j\in [i]$, i.e. the first $i$ coordinates of a solution in level $i$ are integral, (b) $\sum_{[x,\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$, (c) $\sum_{[x,\lambda]\in L_i}\lambda x \leq x^*$, (d) $|L_i|\leq t$.
\end{lemma}
\begin{proof}
	We prove this lemma using induction but one can see how to turn this proof into a polynomial time algorithm. Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $x^*$ and multiplier 1. All the requirements in the lemma are satisfied for this choice.

	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$. Let the solutions in $L_i$ be $x^j$ for $j\in [k]$ and $\lambda_j$ be their multipliers, respectively. For each $j\in[k]$ if $x^j_{i+1}=1$ we add the pair $(x^j,\lambda_j)$ to $L'$. Otherwise,	applying Lemma \ref{round-up} (setting $x'= x^j$ and $\ell = i+1$) we can find $x^{j0}$, $x^{j1}$, $\lambda^0_j$ and $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}. Add the pairs  $(x^{j0} ,\lambda_j\lambda^0_j)$ and  $(x^{j1} ,\lambda_j\lambda^1_j)$ to $L'$. The set $L'$ is a suitable candidate for $L_{i+1}$, i.e. set $L'$ satisfies (a), (b) and (c). However we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$. We call the following linear program $\prun(L')$. Let $L' = \{[x^1,\gamma_1],\ldots,[x^{|L'|},\gamma_{|L'|}]\}$. The variables of $\prun(L')$ are scalar variables $\theta_j$ for each node $j$ in $L'$.  
		\begin{equation}
		\prun(L')\quad\quad\quad \{\max \sum_{j=1}^{|L'|} \theta_j\;:\; \sum_{j=1}^{|L'|} \theta_j x^j_i\leq x^*_i \mbox{ for $i\in [t]$},\; \theta\geq 0 \}
		\end{equation}

@@

	\paragraph{From the leaves of FDT to feasible solutions.}
	For the leaves of the FDT tree,  $L_t$, we have that every solution $x$ in $L_t$ has $x\in\{0,1\}^n$ and $x\in \dom(P)$. By applying Lemma \ref{domlemma} we can obtain a point $x'\in S$ such that $x'\leq x$. This concludes the description of the FDT algorithm and proves Theorem \ref{binaryFDT}. See Algorithm \ref{FDTFull} for a summary of the FDT algorithm.

@@

\begin{proof}
	Consider the following LP with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
	\begin{align}
	\quad\quad& \max\quad \;\sum_{j=0,1,2}\lambda_j\\
	&\;\text{s.t.} \quad x^j(\delta(U))\geq 2\lambda_j \;& \mbox{ for $\emptyset \subset U \subset V$, and $j=0,1,2$} \label{feasibility2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq 2\lambda_j\; &\mbox{ for $j=0,1,2$}\label{bound2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^j_e =j\cdot \lambda_j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq \lambda_j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1+x^2 \leq x\label{packing2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1,\lambda_2 \geq 0
	\end{align}	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above. Let $\hat{x}^{j}={x^j}/{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$. If $\gamma_j=0$, let $\hat{x}^{j}=0$. Observe that  (ii), (iii), (iv), and (v) are satisfied with this choice. We can also show that $\gamma_0+\gamma_1+\gamma_2\geq {1}/{g(\2ec)}$, which means that (i) is also satisfied. The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 1$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.	
	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1+\gamma_2\geq \frac{1}{g(\2ec)}$.
	\end{claim}
	\begin{cproof}
		Suppose for contradiction $\sum_{j=0,1,2}\gamma_j = \frac{1}{g(\2ec)} - \epsilon$ for some $\epsilon >0$. Construct graph $G'$ by removing edge $f$ with $x_f\geq 1$ and replacing it with a path $P_f$ of length $\ceil{\frac{2}{\epsilon}}$. Define $x'_h = x_h$ for each edge $h$ such that $x_h<1$. For each $h\in P_f$ let $x'_h= x_f$ for all $f$ with $x_f\geq 1$. We have $x'\in \subtour(G')$. By Theorem \ref{CV2} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multi-subgraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that 
		$\sum_{i=1}^{k}\theta_i \chi^{F'_i}\leq g(\2ec)x'$.
